Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-26 paper.tex
loni summary

        \subsection{Pipeline description}
        LONI uses the dataflow programming model to represent the pipeline. Data
flows between \textit{Modules} through \textit{data pipes}. Sub-pipelines are
known and \textit{Pipelets}. Modules are defined by the input arguments/streams
and output arguments/stream. Arguments in LONI may be specific
filetypes, flags or values listed in the order in which the application
requires. The provided arguments may be required or optional and can also be
duplicated, if necessary. List of inputs may also be provided to process
multiple inputs with copies of the same module in parallel (batch processing). Conversely, it is
also possible to group list of inputs so as to process them all by the single
module \note{Need to express this better}. Input/Output arguments may be added
to the table of global variables for easy access throughout the pipeline. It is
possible to apply variable modifiers to the variables stored within the table.   
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Automatic Analysis}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Dipy}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

        \subsection{Pipeline description}
        LONI uses the dataflow programming model to represent the pipeline. Data
flows between \textit{Modules} through \textit{data pipes}. Sub-pipelines are
known and \textit{Pipelets}. Modules are defined by the input arguments/streams
and output arguments/stream. Arguments in LONI may be specific
filetypes, flags or values listed in the order in which the application
requires. The provided arguments may be required or optional and can also be
duplicated, if necessary. File inputs in the form of URLs are accepted by LONI
and will be downloaded at runtime. List of inputs may also be provided to process
multiple inputs with copies of the same module in parallel (batch processing). Conversely, it is
also possible to group list of inputs so as to process them all by the single
module \note{Need to express this better}. Input/Output arguments may be added
to the table of global variables for easy access throughout the pipeline. It is
possible to apply variable modifiers to the variables stored within the table.

Intermediary outputs as well as the file output are treated as temporary by
LONI. They are scheduled for deletion before a new pipeline is executed. It is,
however, possible to preserve these files.

        \subsection{Pipeline execution}
        As a
module completes it execution, its output gets transmitted through the dataflow
and the dependent modules are signaled that their input data has arrived.
Modules who have met all their dependency requirements are ready for execution.
Should a module have no dependecies, it can be executed immediately. Modules
ready to be executed are placed in a FIFO launch queue to avoid straining the
platform.

       LONI offers a built in client/server strategy that uses Java's remote
method invocation (RMI) libraries to communicate between servers. This enables
modules, pipelets or pipelines to be executed on servers different from the
client. It also enables full pipelines to consist of connected modules and
pipelets located on different servers. It is favorable to have such a
configuration in LONI, as the tools required for processing may not be available
on client server, but located in another. The client is responsible for
dictating all file transfers and module launches that are to occur. The client
authenticates with the servers through a one-way hash. Only files produced by
the pipeline are accessible to the client and only temporary files created by
the server may be written to the server.

        \subsection{Debugging and provenance}
        For each dataset processed in a LONI pipeline, there exists a corresponding
provenance (.prov) XML file. The \textit{Provenance Editor}, a standalone
platform-independent application, reads the metadata from the image headers,
extracts relevant provenance information from them and creates the provenance files. 
This data can be modified by the user in the to correct inaccuracies or append
additional details before being saved. During pipeline execution, the provenance
file will be edited by the LONI pipeline to include details on each processing
step, the environment in which the data was processed and tool binaries used. 
    \section{Automatic Analysis}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Dipy}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
